Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-07 paper/structureScene.tex
page budget
typo

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Object-based Auditory Scenes Similarity and Classification Using Scattering Features}

@@

In following experiments, we deterministically set $\alpha$ to the values $-1$, $\frac{1}{2}$, $0$, $+\frac{1}{2}$, and $+1$.
This is a form of data augmentation, because $5$ monophonic signals are derived from each binaural recording in the training set.
At test time, only the center mix ($\alpha = 0$) is used to perform the class.

@@

@@

@@

@@

\section{Discussion}

ML

@@

ML

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
%\title{An evaluation framework for event detection using a morphological model of acoustic scenes}
\title{Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms}

@@

In following experiments, we deterministically set $\alpha$ to the values $-1$, $\frac{1}{2}$, $0$, $+\frac{1}{2}$, and $+1$.
This is a form of data augmentation, because $5$ monophonic signals are derived from each binaural recording in the training set.
At test time, only the center mix ($\alpha = 0$) is used to predict the class.

@@

\ml{GL 2 colonnes}

@@

\ml{GL 1 colonne}

@@

\ml{VL 2 colonnes}

@@

@@

\ml{ML 1/2 colonne}
